\documentclass[a4paper,12pt]{letter}
\pagestyle{empty}
\usepackage[utf8]{inputenc}
%\usepackage[polish]{babel}
%\usepackage{polski}
%\usepackage[T1]{fontenc}
%\usepackage{marvosym}
%\usepackage{fontspec} 			

\frenchspacing
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=9in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin



\begin{document} 
\begin{letter}{Robert Ospara \\ ul. Przemyska 24C/8 \\ 80-180 Gda\'{n}sk \\ phone: 783010280 \\ e-mail: robertospara@gmail.com}


\opening{Dear Sir/Madam,} 
 
I would like to submit my application to the offer of software development engineer
in Your company.

At the moment I work for the software house Infoprojekt sp. z o.o. in Gda\'{n}sk. I develop enterprise systems and web applications.
During my all career I was also creating Sharepoint solutions, DTV software and financial systems. 
I studied at the Department of Mathematics and Computer Science at the University of Nicolai Copernicus in Torun/Poland and graduated with 
diploma of master of computer science.

In relationships to other people I'm friendly, frank and honest person.
I am ambitious, curious about other people and the World itself. My main features of character are: patience, 
precision, meticulous, exactitude and continuous striving after perfection. I do love to get to know new things and 
I’m open-minded person, especially about new solutions and new ways of thinking. I do love new challenges, especially the hard ones. 
I’m interested in new techs, physics, astronomy, basketball, martial arts and chess. 

My main goal in applying for this job is to support this company with my knowledge, my hard work and my personal gifts. 
I dream about creating new value of life for mankind by discoveries that can be done by this opportunity. 
I'd like to widen range of my skills and continuously extend my professional qualifications. 
I believe that working for You will be very interesting time and it will give us a lot of joy. 
I hope also that my person is for You enough interesting and soon we will meet together on interview and then 
I will be able to say more about myself and ask some questions about the vacancy.
 
Kind regards, \\
Robert Ospara 


\end{letter}
\end{document}






